\(k\)-Limited Strategies in Banach Mazur Games

### 2017-12-07 postdoctoral/k-markov-tactic-banach-mazur.tex
abandon generalization attempt - will now write up case k=0

  \begin{proof}
    Let \(\tau(\vec p,n)\) be a winning \((k+1)\)-mark for \(\plII\).
    Let \(\preceq\) well-order \(\mb P^{k+1}\).
    For \(f\in\mb P^\omega\), let
    \(f_n=\<f(n),\dots,f(n+k)\>\in\mb P^{k+1}\).
    For \(\vec p,\vec r\in\mb P^{k+1}\) say that \(\vec p\) improves \(\vec r\)
    if for each \(m\leq k\), there exists \(n\leq k\) such that
    \(\vec r(m)\geq\vec p(n)\).

    For \(\vec p\in \mb P^{k+1}\) and \(q\in\mb P\), say \(\vec p\) is
    \(n\)-above \(q\) if there exists \(s_n(\vec p)\in\mb P^{k+1}\)
    improving \(\vec p\)
    such that
    \[
      \vec p(k)
    \geq
      s_n(\vec p)(k)
    \geq
      \tau(s_n(\vec p),n+k)
    \geq
      q
    \]
    (noting \(\vec p(k)\geq s_n(\vec p)(k)\) is just a consequence of
    \(s_n(\vec p)\) improving \(\vec p\)).

    Say \(\vec p\) is \(\omega\)-above \(q\) if \(\vec p\) is \(n\)-above
    \(q\) for all \(n<\omega\). If \(\vec p\) is \(\omega\)-above some
    \(l(\vec p)\), then say \(\vec p\) is long; otherwise call \(\vec p\)
    short. Note any \(\vec p\) improved by a long vector is itself long,
    so any \(\vec p\) improving a short vector is itself short.

    For \(\vec p\) short, let
    \[
      \mu(\vec p)
        =
      \min_{\preceq}\{
        \vec r\text{ short}
          :
        \vec{p}\text{ improves }\vec{r}
      \}
    \]
    and since \(\mu(\vec p)\) is not \(n\)-above \(\vec p\) for some \(n\), let
    \[
      N(\vec p)
        =
      \min\{
        n<\omega
      :
        \mu(\vec p)\text{ is not }n\text{-above }\vec p
      \}
    .\]

    We define
    \[
      \sigma(\vec p)
        =
      \begin{cases}
        \tau(\vec p,|\vec p|-1) & 0<|\vec p|\leq k \\
        l(\vec p) & \vec p \text{ is long} \\
        \tau^{N(\vec p)+1}(\vec p) & \vec p \text{ is short}
     \end{cases}
    .\]

    Suppose \(\sigma\) is legally attacked by \(a\in\mb P^\omega\).
    % Suppose \(b\) is a subsequence of \(a\) where
    % \(b_n\) is long for all \(n<\omega\).
    % Since \(b_n\) improves \(a_n\)
    % for all \(n<\omega\), it follows that
    % \(a_n\) is long for all \(n<\omega\).
    Thus for \(n<k\),
    \[
      a(n)
        \geq
      \tau(a\rest(n+1),n)
        =
      \sigma(a\rest(n+1))
        \geq
      a(n+1)
    .\]
    For \(n\leq\omega\), if \(a_n\) is long, then \(a_n\) is \(n\)-above
    \(l(a_n)\). Therefore,
    \[
      a(n+k)
        =
      a_n(k)
        \geq
      s_n(a_n)(k)
        \geq
      \tau(s_n(a_n),n+k)
        \geq
      l(a_n)
        =
      \sigma(a_n)
        \geq
      a(n+k+1)
    .\]
    Thus if \(a_n\) is long for \(n<\omega\), it follows that  \(\<a(0),\dots,a(k-1),s_0(a_0)(k),s_1(a_1)(k),\dots\>\)
    is a legal attack against \(\tau\). Since \(\tau\) is winning,
    this attack belongs to \(W\). Since this attack zips into \(a\),
    \(a\) also belongs to \(W\).

>>>>

  \begin{proof}
    Let \(\tau(\vec p,n+1)\) be a winning \((k+1)\)-mark for \(\plII\),
    where \(n+1\) is the number of moves previously made by \(\plI\).
    Let \(\preceq\) well-order \(\mb P^{k+1}\).
    For \(f\in\mb P^\omega\), let
    \(f_n=\<f(n),\dots,f(n+k)\>\in\mb P^{k+1}\).

    For \(\vec p\in \mb P^{k+1}\) and \(q\in\mb P\), say \(\vec p\) is
    \(n\)-above \(q\) if there exists \(s_n(\vec p)\in\mb P\)
    such that
    \[
      \vec p(k)
    \geq
      s_n(\vec p)
    \geq
      \tau(\vec r\concat\<s_n(\vec p)\>,n+k+1)
    \geq
      q
    \]
    for all \(\vec r\in\mb P^k\) ``between \(\vec p(0)\) and \(\vec p(k)\)''.

    For \(\vec p\in\mb P^{k+1}\), let \(t^0(\vec p)=\vec p\),
    \(\tau^{n+1}(\vec p)=\tau(t^n(\vec p),n+1)\), and
    \(t^{n+1}(\vec p)=(t^n(\vec p)\last k)\concat\<\tau^{n+1}(\vec p)\>\).

    Say \(\vec p\) is \(\omega\)-above \(q\) if \(\vec p\) is \(n\)-above
    \(q\) for all \(n<\omega\). If \(\vec p\) is \(\omega\)-above some
    \(l(\vec p)\), then say \(\vec p\) is long; otherwise call \(\vec p\)
    short.

    For \(\vec p\) short, let
    \[
      \mu(\vec p)
        =
      \min_{\preceq}\{
        \vec r\text{ short}
          :
        \vec{r}(k)\geq\vec{p}(k)
      \}
    \]
    and since \(\mu(\vec p)\) is not \(n\)-above \(\vec p(k)\) for some \(n\),
    let
    \[
      N(\vec p)
        =
      \min\{
        n<\omega
      :
        \mu(\vec p)\text{ is not }n\text{-above }\vec p(k)
      \}
    .\]

    We define
    \[
      \sigma(\vec p)
        =
      \begin{cases}
        \tau(\vec p,|\vec p|) & |\vec p|\leq k \\
        l(\vec p) & \vec p \text{ is long} \\
        \tau^{N(\vec p)+1}(\vec p) & \vec p \text{ is short}
     \end{cases}
    .\]

    Suppose \(\sigma\) is legally attacked by \(a\in\mb P^\omega\).
    % Suppose \(b\) is a subsequence of \(a\) where
    % \(b_n\) is long for all \(n<\omega\).
    % Since \(b_n\) improves \(a_n\)
    % for all \(n<\omega\), it follows that
    % \(a_n\) is long for all \(n<\omega\).
    Thus for \(n<k\),
    \[
      a(n)
        \geq
      \tau(a\rest(n+1),n)
        =
      \sigma(a\rest(n+1))
        \geq
      a(n+1)
    .\]
    For \(n\leq\omega\), if \(a_n\) is long, then \(a_n\) is \(n\)-above
    \(l(a_n)\). Therefore,
    \[
      a(n+k)
        =
      a_n(k)
        \geq
      s_n(a_n)
        \geq
      \tau((a_n\last k)\concat\<s_n(a_n)\>,n+k)
        \geq
      l(a_n)
        =
      \sigma(a_n)
        \geq
      a(n+k+1)
    .\]
    Thus if \(a_n\) is long for \(n<\omega\), it follows that  \(\<a(0),\dots,a(k-1),s_0(a_0)(k),s_1(a_1)(k),\dots\>\)
    is a legal attack against \(\tau\). Since \(\tau\) is winning,
    this attack belongs to \(W\). Since this attack zips into \(a\),
    \(a\) also belongs to \(W\).
